Respiratory oacsteroids

### 2021-03-06 r_notebooks/preparing_differences/preparing_contra.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

```{r contra-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

contra <- 
  read_rds("../data/presdata_updates_040121/presc_wales_contra-combined.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practice_id))

@@

## Identify GPs with missing data 
gp_missing <- 
  contra_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
contra_monthly_count_pre_cv19 <- 
  contra_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

contra_monthly_quantity_gp_pre_cv19 <- 
  contra_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
contra_monthly_count_pre_cv19 <- 
  contra_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(contra_monthly_count_pre_cv19)

contra_monthly_quantity_gp_pre_cv19 <- 
  contra_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(contra_monthly_quantity_gp_pre_cv19)

@@

```{r, contra-gp-practice-modelling}
plan(cluster)
system.time(contra_gp_cv_models <-
  contra_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

contra_gp_cv_models %>%
  saveRDS("../data/contra_gp_cv_models.rds")

contra_gp_cv_models <- 
  read_rds("../data/contra_gp_cv_models.rds")

contra_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

contra_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r contra-gp-modelling-accuracy}
best_model_gp <- 
  contra_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

@@

```{r contra-gp-practice-forecasts}
plan(cluster)
system.time(contra_gp_fcsts <-
              contra_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

contra_gp_fcsts %>%
  saveRDS("../data/contra_gp_fcsts.rds")

contra_gp_fcsts <- 
  read_rds("../data/contra_gp_fcsts.rds")

@@

```{r, contra-gp-practice-discrepancies}
best_model_gp <- 
  contra_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../data/differences/contra_discreps.rds")

>>>>

```{r contra-data}
gp <- 
  read_rds("../../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

contra <- 
  read_rds("../../data/presdata_updates_040121/presc_wales_contra-combined.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practice_id))

@@

## Identify GPs with missing data 
gp_missing <- 
  contra_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
contra_monthly_count_pre_cv19 <- 
  contra_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

contra_monthly_quantity_gp_pre_cv19 <- 
  contra_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

## Replace missing values in training data
contra_monthly_count_pre_cv19 <- 
  contra_monthly_count_pre_cv19 %>% 
  model(arima = ARIMA(n)) %>%
  interpolate(contra_monthly_count_pre_cv19)

contra_monthly_quantity_gp_pre_cv19 <- 
  contra_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(arima = ARIMA(n)) %>% 
  interpolate(contra_monthly_quantity_gp_pre_cv19)

@@

```{r, contra-gp-practice-modelling}
plan(cluster)
system.time(contra_gp_cv_models <-
  contra_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 36, step = 3))
plan(sequential)

contra_gp_cv_models %>%
  saveRDS("../../data/contra_gp_cv_models.rds")

contra_gp_cv_models <- 
  read_rds("../../data/contra_gp_cv_models.rds")

contra_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

contra_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r contra-gp-modelling-accuracy}
best_model_gp <- 
  contra_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE)

@@

```{r contra-gp-practice-forecasts}
plan(cluster)
system.time(contra_gp_fcsts <-
              contra_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "8 months"))
plan(sequential)

contra_gp_fcsts %>%
  saveRDS("../../data/contra_gp_fcsts.rds")

contra_gp_fcsts <- 
  read_rds("../../data/contra_gp_fcsts.rds")

@@

```{r, contra-gp-practice-discrepancies}
best_model_gp <- 
  contra_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../../data/differences/contra_discreps.rds")

### 2021-03-06 r_notebooks/preparing_differences/preparing_nsaid.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

```{r nsaid-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

nsaid <- 
  read_rds("../data/presdata_updates_040121/presc_wales_NSAIDs.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))

@@

## Identify GPs with missing data 
gp_missing <- 
  nsaid_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
nsaid_monthly_count_pre_cv19 <- 
  nsaid_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

nsaid_monthly_quantity_gp_pre_cv19 <- 
  nsaid_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
nsaid_monthly_count_pre_cv19 <- 
  nsaid_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(nsaid_monthly_count_pre_cv19)

nsaid_monthly_quantity_gp_pre_cv19 <- 
  nsaid_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(nsaid_monthly_quantity_gp_pre_cv19)

@@

```{r, nsaid-gp-practice-modelling}
plan(cluster)
system.time(nsaid_gp_cv_models <-
  nsaid_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

nsaid_gp_cv_models %>%
  saveRDS("../data/nsaid_gp_cv_models.rds")

nsaid_gp_cv_models <- 
  read_rds("../data/nsaid_gp_cv_models.rds")

nsaid_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

nsaid_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r nsaid-gp-modelling-accuracy}
best_model_gp <- 
  nsaid_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

@@

```{r nsaid-gp-practice-forecasts}
plan(cluster)
system.time(nsaid_gp_fcsts <-
              nsaid_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

nsaid_gp_fcsts %>%
  saveRDS("../data/nsaid_gp_fcsts.rds")

nsaid_gp_fcsts <- 
  read_rds("../data/nsaid_gp_fcsts.rds")

@@

```{r, nsaid-gp-practice-discrepancies}
best_model_gp <- 
  nsaid_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../data/differences/nsaid_discreps.rds")

>>>>

```{r nsaid-data}
gp <- 
  read_rds("../../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

nsaid <- 
  read_rds("../../data/presdata_updates_040121/presc_wales_NSAIDs.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))

@@

## Identify GPs with missing data 
gp_missing <- 
  nsaid_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
nsaid_monthly_count_pre_cv19 <- 
  nsaid_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

nsaid_monthly_quantity_gp_pre_cv19 <- 
  nsaid_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

## Replace missing values in training data
nsaid_monthly_count_pre_cv19 <- 
  nsaid_monthly_count_pre_cv19 %>% 
  model(arima = ARIMA(n)) %>%
  interpolate(nsaid_monthly_count_pre_cv19)

nsaid_monthly_quantity_gp_pre_cv19 <- 
  nsaid_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(arima = ARIMA(n)) %>% 
  interpolate(nsaid_monthly_quantity_gp_pre_cv19)

@@

```{r, nsaid-gp-practice-modelling}
plan(cluster)
system.time(nsaid_gp_cv_models <-
  nsaid_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 36, step = 3))
plan(sequential)

nsaid_gp_cv_models %>%
  saveRDS("../../data/nsaid_gp_cv_models.rds")

nsaid_gp_cv_models <- 
  read_rds("../../data/nsaid_gp_cv_models.rds")

nsaid_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

nsaid_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r nsaid-gp-modelling-accuracy}
best_model_gp <- 
  nsaid_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE)

@@

```{r nsaid-gp-practice-forecasts}
plan(cluster)
system.time(nsaid_gp_fcsts <-
              nsaid_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "8 months"))
plan(sequential)

nsaid_gp_fcsts %>%
  saveRDS("../../data/nsaid_gp_fcsts.rds")

nsaid_gp_fcsts <- 
  read_rds("../../data/nsaid_gp_fcsts.rds")

@@

```{r, nsaid-gp-practice-discrepancies}
best_model_gp <- 
  nsaid_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../../data/differences/nsaid_discreps.rds")

### 2021-03-06 r_notebooks/preparing_differences/preparing_oac_prop.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

```{r oac-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

oac <- 
  read_rds("../data/presdata_updates_040121/presc_wales_OAC.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = yearmonth(dmy(paste0("28-", datename))),
         practice_id = as_factor(practice_id))

@@

oac_monthly_prop_gp_pre_cv19 <- 
  oac_monthly_prop_gp %>% 
  filter(datename < yearmonth("2020 March"))

oac_monthly_prop_gp_pre_cv19 <- 
  oac_monthly_prop_gp_pre_cv19 %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  pivot_longer(cols = `2015 Jan`:`2020 Feb`, 
               names_to = "datename", values_to = "n", 
               values_drop_na = FALSE) %>% 
  mutate(datename = yearmonth(datename)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(oac_monthly_prop_gp_pre_cv19) %>% 
  filter(!regional_unit %in% # Remove those with <62 months data
           (oac_monthly_prop_gp_pre_cv19 %>% 
              as_tibble %>% 
              ungroup() %>% 
              group_by(regional_unit) %>% 
              count() %>% 
              filter(n < 62) %>% 
              .$regional_unit) &
           !regional_unit %in% # Remove bottom 10% GPs by total oac volume 
           (oac %>% 
              group_by(practice_id) %>% 
              summarise(tot_quant = sum(quantity)) %>% 
              arrange(tot_quant) %>% 
              slice_tail(prop = .1))) 
```

@@

```{r, oac-gp-practice-modelling}
plan(cluster)
system.time(oac_gp_cv_models <-
  oac_monthly_prop_gp_pre_cv19 %>%
                  regionalCVBound(init = 48, step = 3))
plan(sequential)

oac_gp_cv_models %>%
  saveRDS("../data/oac_gp_cv_models.rds")

oac_gp_cv_models <- 
  read_rds("../data/oac_gp_cv_models.rds")

oac_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

oac_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r oac-gp-modelling-accuracy}
best_model_gp <- 
  oac_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

@@

```{r oac-gp-practice-forecasts}
plan(cluster)
system.time(oac_gp_fcsts <-
              oac_monthly_prop_gp_pre_cv19 %>%
              regionalJointFcstsBound(h = "6 months"))
plan(sequential)

oac_gp_fcsts %>%
  saveRDS("../data/oac_gp_fcsts.rds")

oac_gp_fcsts <- 
  read_rds("../data/oac_gp_fcsts.rds")

@@

```{r, oac-gp-practice-discrepancies}
best_model_gp <- 
  oac_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../data/differences/oac_discreps.rds")
```

>>>>

```{r oac-data}
gp <- 
  read_rds("../../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

oac <- 
  read_rds("../../data/presdata_updates_040121/presc_wales_OAC.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = yearmonth(dmy(paste0("28-", datename))),
         practice_id = as_factor(practice_id))

@@

oac_monthly_prop_gp_pre_cv19 <- 
  oac_monthly_prop_gp %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

oac_monthly_prop_gp_pre_cv19 <- 
  oac_monthly_prop_gp_pre_cv19 %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  pivot_longer(cols = `2015 Jan`:`2020 Feb`, 
               names_to = "datename", values_to = "n", 
               values_drop_na = FALSE) %>% 
  mutate(datename = yearmonth(datename)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  group_by(regional_unit) %>% 
  model(arima = ARIMA(n)) %>% 
  interpolate(oac_monthly_prop_gp_pre_cv19) %>% 
  filter(!regional_unit %in% # Remove those with <60 months data
           (oac_monthly_prop_gp_pre_cv19 %>% 
              as_tibble %>% 
              ungroup() %>% 
              group_by(regional_unit) %>% 
              count() %>% 
              filter(n < 60) %>% 
              .$regional_unit) &
           !regional_unit %in% # Remove bottom 10% GPs by total oac volume 
           (oac %>% 
              group_by(practice_id) %>% 
              summarise(tot_quant = sum(quantity)) %>% 
              arrange(tot_quant) %>% 
              slice_tail(prop = .1))) 
```

@@

```{r, oac-gp-practice-modelling}
plan(cluster)
system.time(oac_gp_cv_models <-
  oac_monthly_prop_gp_pre_cv19 %>%
                  regionalCVBound(init = 36, step = 3))
plan(sequential)

oac_gp_cv_models %>%
  saveRDS("../../data/oac_gp_cv_models.rds")

oac_gp_cv_models <- 
  read_rds("../../data/oac_gp_cv_models.rds")

oac_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

oac_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r oac-gp-modelling-accuracy}
best_model_gp <- 
  oac_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE)

@@

```{r oac-gp-practice-forecasts}
plan(cluster)
system.time(oac_gp_fcsts <-
              oac_monthly_prop_gp_pre_cv19 %>%
              regionalJointFcstsBound(h = "8 months"))
plan(sequential)

oac_gp_fcsts %>%
  saveRDS("../../data/oac_gp_fcsts.rds")

oac_gp_fcsts <- 
  read_rds("../../data/oac_gp_fcsts.rds")

@@

```{r, oac-gp-practice-discrepancies}
best_model_gp <- 
  oac_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../../data/differences/oac_discreps.rds")
```
